Weakly Nonlinear MRI: Notes

### 2014-05-29 notes/mri_notes.tex
adjoint homogenous eqn
equations coded in dedalus

%\usepackage[numbers]{natbib}
\usepackage{natbib}
\bibliographystyle{apj}
%\setlength{\bibsep}{0.0pt}

@@

>>>>

%\usepackage[numbers]{natbib}
\usepackage{natbib}
\bibliographystyle{apj}
%\setlength{\bibsep}{0.0pt}
\usepackage{courier}

@@

Now we will actually solve the adjoint homogenous first-order equation, that is: \\

Where $\mathcal{L}^\dagger = \mathcal{L}_0^T \, - \, \mathcal{L}_1^T \partial_z \, + \, \mathcal{L}_2^T\partial_z^2 \, - \, \mathcal{L}_3^T \partial_z^3 \, + \, \mathcal{L}_4^T \partial_z^4$ \\

And $\mathcal{L}_0^T = \mathcal{L}_0$, $\mathcal{L}_2^T = \mathcal{L}_2$, $\mathcal{L}_4^T = \mathcal{L}_4$ because these are diagonal matrices. We also have:\\

$\mathcal{L}_1^T = \left[\begin{matrix}
0 & 2-q & 1 & 0 \\
2 & 0 & 0 & 1 \\
\frac{1}{4\pi} \partial_x^2 & 0 & 0 & -q\\
0 & \frac{1}{4\pi} & 0 & 0 \\
\end{matrix}\right]$ \\

$\mathcal{L}_3^T = \left[\begin{matrix}
0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 \\
\frac{1}{4\pi} & 0 & 0 & 0\\
0 & 0 & 0 & 0 \\
\end{matrix}\right]$ \\

Writing out the expressions, where $\mathbf{V}^\dagger = \left[\Psi^\dagger, u^\dagger, A^\dagger, B^\dagger\right]^T$, we have: \\

$\frac{1}{\reye}\partial_x^4 \Psi^\dagger \, - \, (2-q)\partial_z u^\dagger \, - \, \partial_z A^\dagger \, + \, \frac{2}{\reye}\partial_x^2 \partial_z^2 \Psi^\dagger \, + \, \frac{1}{\reye}\partial_z^4 \Psi^\dagger \, = \, 0$ \\

$\frac{1}{\reye}\partial_x^2 u^\dagger \, - \, 2 \partial_z \Psi^\dagger \, - \, \partial_z B^\dagger, \, + \, \frac{1}{\reye}\partial_z^2 u^\dagger \, = \, 0$ \\

$\frac{1}{\reym} \partial_x^2 A^\dagger \, - \, \frac{1}{4\pi} \partial_x^2 \partial_z \Psi^\dagger \, + \, q \partial_z B^\dagger  \,+ \, \frac{1}{\reym} \partial_z^2 A^\dagger \, - \, \frac{1}{4\pi} \partial_z^3 \Psi^\dagger \, = \, 0$ \\

$\frac{1}{\reym} \partial_x^2 B^\dagger \, - \, \frac{1}{4\pi} \partial_z u^\dagger \, + \, \frac{1}{\reym} \partial_z^2 B^\dagger \, = \, 0$ \\

We will use the linear eigenvalue solver in Dedalus to determine $\mathbf{V}^\dagger$. \\

At marginality, the z-dependence is given by $e^{iQz}$. Thus the above equations become a system of PDEs in x for the fluid quantities: \\

$\frac{1}{\reye}\partial_x^4 \Psi^\dagger \, - \, (2 - q) i Q u^\dagger \, - \,  i Q A^\dagger \, - \, Q^2 \frac{2}{\reye} \partial_x^2 \Psi^\dagger \, + \, Q^4 \frac{1}{\reye} \Psi^\dagger \, = \, 0$ \\

$\frac{1}{\reye}\partial_x^2 u^\dagger \, - \, 2 i Q \Psi^\dagger \, - \, i Q B \, - \frac{1}{\reye} Q^2 u^\dagger \, = \, 0$ \\

$\frac{1}{\reym} \partial_x^2 A^\dagger \, - \, \frac{1}{4\pi} i A \partial_x^2 \Psi^\dagger \, + \, q i Q B^\dagger \, - \, Q^2 \frac{1}{\reym} A^\dagger \, + \, i Q^3 \frac{1}{4\pi} \Psi^\dagger \, = \, 0$ \\

$\frac{1}{\reym} \partial_x^2 B^\dagger \, - \, \frac{1}{4\pi} i Q u^\dagger \, - \, Q^2 \frac{1}{\reym} B^\dagger \, = \, 0$ \\

The above is coded up in \texttt{adjoint\_homogenous.py}.
